%!TEX root = ../resume.tex

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Assistant \& Teaching Assistant (Prof. Sylvain Hallé)} % Job title
    {UQAC (Université du Québec à Chicoutimi)} % Organization
    {Chicoutimi, Québec, Canada} % Location
    {Aug. 2014 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed a set of algorithms to evaluate LTL formul\ae{}s by manipulating Bitmaps and implemented them with Java.}
        \item {Implemented a one-way communication channel with optical codes.}
        \item {Developed a software suite to import and synchronize a geoname database for a research project with the engineers from \href{http://solutionstlm.com/}{TLM}.}
        \item {Took part in writing two papers for publication.}
        \item {Evaluated homework and tests of the students.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Advisory Researcher} % Job title
    {Lenovo} % Organization
    {Beijing, China} % Location
    {Aug. 2010 - Jan. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented a distributed storage system supporting scalability, load-balancing, fail-over, cross-datacenter replication, log collection and analysis. Key customers include government, banks, and financial and assurance companies.}
        \item {Built technology road map and strategic direction for the product.}
        \item {Led a team of 10 engineers and established a Scrum project management process.}
        \item {Developed with C, C++, Go lang, PHP, Thrift, ProcotolBuffer, etc.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Oak Pacific Interactive} % Organization
    {Beijing, China} % Location
    {Jul. 2009 - Aug. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed the vertical search engine of the SNS website \url{http://renren.com}, including distributed indexing, distributed searching, ranking system (weighted ranking and 2 dimensions ranking).}
        \item {Run the engine on a server cluster across 60+ servers, and the engine had to process over 40 million requests per day.}
        \item {Led a team of 5 engineers.}
        \item {Developed with C++, Java and the RPC framework Zeroc ICE.}
      \end{cvitems} 
    }

%---------------------------------------------------------
  \cventry
    {Technical Director \& Co-Founder} % Job title
    {Width Technologies} % Organization
    {Beijing, China} % Location
    {Apr. 2007 - Jul. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team of 7 engineers to design and implement an Internet storage website (like MegaUpload) which served 1 million visitors per day and 4 terabytes traffic (upload \& download) per day.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Kuxun Technologies} % Organization
    {Beijing, China} % Location
    {Jul. 2006 - Apr. 2007} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a load-balancing cache server (like haproxy), used for caching the static content, fetching, merging and caching the searching results. The cache cluster served a load of 2 million visits in the peak hour.}
        \item {Developed a classic inverted-index searching engine, each of which could support 300 requests per second.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {AscentVision} % Organization
    {Tianjin, China} % Location
    {Nov. 2004, - Jul. 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyzed various application‐layer network protocols (MSN, torrent, emule, Skype, etc) and developed the Linux kernel modules to identify and control the traffic of them.}
        \item {Developed the Linux kernel modules, used for a network tunnel supporting real-time data compression.}
        \item {Developed the Linux kernel modules to control the flow of the applications.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
